Kaggle-in-class Data Challenges Can Boost Student Learning

### 2018-05-10 paper-kaggle.Rmd
engagement completed

The number of submissions that a student made, may be an indicator of performance on the exam questions related to the competition.  A student who is more engaged in the competition may learn more about the material, and consequently perform better on the exam. Figure \ref{fig:numsubmition} shows normalized scores and overall exam scores, against frequency of prediction submissions for the MAST90083 competitions.

@@

```{r numsubmition, echo = FALSE, fig.cap = "\\label{fig:numsubmition} Scatterplot of the normalised scores, and exam scores, by number of prediction submissions for MAST90083. " , fig.width=6, fig.height=3}

UniMelbData_long <- UniMelbData %>%
  gather(questype, score, ptq_class, pte_class, ptq_reg, pte_reg) %>%
  separate(questype, c("normtype", "questype")) %>%
  mutate(questype=fct_recode(questype, "classification"="class", "regression"="reg"))
ggplot(filter(UniMelbData_long, normtype=="ptq"), aes(x=numsub, y=score)) + 
  geom_point() + facet_wrap(~questype, ncol=2, scales="free_y") +
  geom_smooth(method="lm", se=FALSE) + 
  ylab("Normalized scores") + 
  xlab("Number of submissions")
```

>>>>

The number of submissions that a student made, may be an indicator of performance on the exam questions related to the competition.  A student who is more engaged in the competition may learn more about the material, and consequently perform better on the exam. Figure \ref{fig:numsubmition} shows performance on the classification and regression questions, respectively, against their frequency of prediction submissions for the three student groups (MAST90083 classification and regression, ETC5242 regression) competitions. The relationship is weak in all groups, and this mirrors insignificant results from a linear model fit to both subsets. On the other hand, the predictive accuracy improved with the number of submissions for the regression competitions.

@@

```{r numsubmition, echo = FALSE, fig.cap = "\\label{fig:numsubmition} Scatterplot of the performance by number of prediction submissions, for three student groups. The relationships with exam performance are weak. For the MAST90083 and ETC5242 regression competitions, a clear pattern is that predictions improved substantially with more submissions." , fig.width=6, fig.height=6}
etc5242 <- read_csv("data/competition_5242.csv")
scores_5242_comp <- scores_5242 %>% left_join(etc5242, by="id")
p1 <- ggplot(filter(UniMelbData, Proj_alloc == "classification"), aes(x=numsub, y=perf_class)) +
  geom_point() +
  geom_smooth(method="lm", se=FALSE) + 
  ylab("Performance on classification Qs") + 
  xlab("Number of submissions") +
  xlim(c(1,5)) + ggtitle("a. MAST90083 cls")
p2 <- ggplot(filter(UniMelbData, Proj_alloc == "regression"), aes(x=numsub, y=perf_reg)) +
  geom_point() +
  geom_smooth(method="lm", se=FALSE) + 
  ylab("Performance on regression Qs") + 
  xlab("Number of submissions") +
  xlim(c(1,12)) + ggtitle("b. MAST90083 reg")
p3 <- ggplot(scores_5242_comp, aes(x=numsub, y=perf)) +
  geom_point() +
  geom_smooth(method="lm", se=FALSE) + 
  ylab("Performance") + 
  xlab("Number of submissions") + ggtitle("c. ETC5242")
#grid.arrange(p1, p2, ncol=2)
p4 <- ggplot(filter(UniMelbData, Proj_alloc == "classification"), aes(x=numsub, y=PrivetScore)) +
  geom_point() +
  geom_smooth(method="lm", se=FALSE) + 
  ylab("Accuracy of predictions") + 
  xlab("Number of submissions") +
  xlim(c(1,5)) + ggtitle("d. MAST90083 cls")
p5 <- ggplot(filter(UniMelbData, Proj_alloc == "regression"), aes(x=numsub, y=PrivetScore)) +
  geom_point() +
  geom_smooth(method="lm", se=FALSE) + 
  #ylab("Error in predictions") + 
  xlab("Number of submissions") +
  scale_y_continuous("Error in predictions ('0000s)", breaks=seq(110000, 170000, 10000), labels=seq(11,17,1)) + ggtitle("e. MAST90083 reg")
  #xlim(c(1,12))
p6 <- ggplot(scores_5242_comp, aes(x=numsub, y=score)) +
  geom_point() +
  geom_smooth(method="lm", se=FALSE) + 
  ylab("Error in predictions") + 
  xlab("Number of submissions") + ggtitle("f. ETC5242")
grid.arrange(p1, p2, p3, p4, p5, p6, ncol=3)

```

```{r eval=FALSE}
library(broom)
m1 <- lm(perf_class~numsub, data=filter(UniMelbData, Proj_alloc == "classification"))
tidy(m1)
glance(m1)
m2 <- lm(perf_class~numsub, data=filter(UniMelbData, Proj_alloc == "regression"))
tidy(m2)
glance(m2)
```
